---
title: "Introduction to rafliassign4"
author: "Your Name"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to rafliassign4}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

- Overview of the package and what it does.

- Key features or functionalities.

- Why users would find the package useful.

- Installation Instructions

```{r setup}
# First, install the package by go to this github link:
# ETC5523-2024/assignment-4-packages-and-shiny-apps-belajaRProgramming0

# Next, type tis in your R Console:
install.packages("rafliassign4")

# Last, load the library into your workspace (Rmd, qmd, etc.)
library(rafliassign4)
```



- Use Case or Example Workflows

Step-by-step examples of how to use the package’s functions or data.

```{r}
# Example: Generate a boxplot for an attribute
library(ggplot2)
library(tidyverse)

ggplot(cleaned_data, aes(x = Sport, y = Age)) +
  geom_boxplot() +
  labs(title = "Age Distribution by Sport", x = "Sport", y = "Age")

```


Visualizations and Plots (Optional)

Use plots, diagrams, or tables to make it easier for users to understand the results.
Example of a boxplot relevant to your package data:

```{r}
library(ggplot2)
library(tidyverse)

ggplot(cleaned_data %>% filter(Top_1_attr == "ANA"), aes(x = Sport, y = Age)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

